\mytitle

### 2020-04-29 paper.tex
minor edits.

\subsection{The Computational Complexity of WFL-QCOP}

%(linear) problems were formulated and solved using  exact solvers.
Despite the existence of mathematical models for WFLO in the literature~\cite{Zhang2014,donovan2005wind} that are expressive enough to represent $\mathcal{NP}$-hard problems, we are unaware of an explicit treatment of the computational complexity of WFLO.
%However, these solvers should only be used if the problem is computationally hard.
%We are unaware of an existing complexity result for the LS variation of WFLO (our QCOP).
We therefore provide a straightforward proof of the computational complexity of WFL-QCOP.

@@

\subsubsection{QCOP solving methods}
WFLO is a type of strictly convex integer quadratically constrained optimization problem (IQCOP), which is known to be NP-hard \cite{van1981another}. The common exact methods for solving
IQCOPs are tree search \cite{land2010automatic} type algorithms with a variety of techniques to prune sub-trees that definitely do not contain the optimal solution.

@@

\todo{@Arik and Chris: please correct Jason's writing errors}

@@

	\vspace{0.5em}
	\caption{Total Expected Power (kW) after 100 seconds as function of benchmark and method. \todo{@Arik: could you please why we do not mention any optimality here?} }\label{tab:results1}
\end{table}

>>>>

\subsection{The Computational Complexity of WFL-QCOP}
\label{sec:computational}
%(linear) problems were formulated and solved using  exact solvers.
Despite the existence of mathematical models for WFLO in the literature~\cite{Zhang2014,donovan2005wind} that are expressive enough to represent $\mathcal{NP}$-hard problems, we are unaware of an explicit treatment of the computational complexity of WFLO.
%However, these solvers should only be used if the problem is computationally hard.
%We are unaware of an existing complexity result for the LS variation of WFLO (our QCOP).
We therefore provide a straightforward proof of the computational complexity of WFL-QCOP.

@@

\subsubsection{QCOP solving methods}
WFL-QCOP is a type of strictly convex integer 
quadratically constrained optimization problem (IQCOP), which is notorious for its computational complexity~\cite{van1981another}. In fact,
we proved in Section~\ref{sec:computational} that WFL-QCOP is $\mathcal{NP}$-hard. The common exact methods for solving
IQCOPs are tree search \cite{land2010automatic} type algorithms with a variety of techniques to prune sub-trees that definitely do not contain the optimal solution.

@@

\todo{@Chris and Jason: I still feel that we need to say how Gurobi do it (or at least how we think Gurobi does that)}

@@

	\vspace{0.5em}
	\caption{Total Expected Power (kW) after 100 seconds as function of benchmark and method.}\label{tab:results1}
\end{table}
